---
title: "Data from Facebook Confessions Forums"
author: "Adrian Naranjo"
---

<br>

### **Question**: given manually labeled data, *can we predict taboos*?

<br>

### Manually labeled data was given to us. These labels represent taboos and include:

* Academics
* Death
* Drugs
* Excretions
* Medical
* Mental Health
* Money / Financial
* Race_ProtectedGroups
* Sex

#### **Note**: a taboo is not a category. It refers to the **manner** in which a category is presented.

<br>

#### This would NOT have a label: "I like sex." 
#### This WOULD have a label: "“I'm a terrible Christian. I can't stop thinking about sex."

<br>

## A Description of our Labels...


<br>

### Line, word counts

```{r, message=FALSE, echo=FALSE, warning=FALSE}
# Import libraries
library(tidyverse)
library(tokenizers)
library(tm)
library(knitr)
library(ggthemes)
library(tidytext)
library(topicmodels)
library(ldatuning)
```

```{r, message=FALSE, echo=FALSE, warning=FALSE}
# Import data
fcb_data <- read_csv('data/FCB.csv') 
all_tokens <- read_csv('data/all_tokens.csv')

fcb_data <- fcb_data %>%
  filter(!text == 'NA' & !is.na(text)) %>% 
  select(-X1) %>% 
  mutate(label = str_replace(label, 'Mental Health', 'Mental_Health')
         ,label = str_replace(label, 'Money/Financial', 'Money_Financial')
         ,label = str_replace(label, 'Race/Protected Groups', 'Race_ProtectedGroups'))

number_lines <- count(fcb_data, label) %>% rename('num_lines' = 'n')

None <- read_csv('data/None_words.csv', col_names = F)
Sex <- read_csv('data/Sex_words.csv', col_names = F)
Mental_Health <- read_csv('data/Mental_words.csv', col_names = F)
Money_Financial <- read_csv('data/Money_words.csv', col_names = F)
Medical <- read_csv('data/Medical_words.csv', col_names = F)
Drugs <- read_csv('data/Drugs_words.csv', col_names = F)
Race_ProtectedGroups <- read_csv('data/Race_words.csv', col_names = F)
# Excretions <- read_csv('data/Excretions_words.csv', col_names = F)
Academics <- read_csv('data/Academics_words.csv', col_names = F)
Death <- read_csv('data/Death_words.csv', col_names = F)

None_clean <- read_csv('data/None_words_clean.csv', col_names = F)
Sex_clean <- read_csv('data/Sex_words_clean.csv', col_names = F)
Mental_Health_clean <- read_csv('data/Mental_words_clean.csv', col_names = F)
Money_Financial_clean <- read_csv('data/Money_words_clean.csv', col_names = F)
Medical_clean <- read_csv('data/Medical_words_clean.csv', col_names = F)
Drugs_clean <- read_csv('data/Drugs_words_clean.csv', col_names = F)
Race_ProtectedGroups_clean <- read_csv('data/Race_words_clean.csv', col_names = F)
# Excretions_clean <- read_csv('data/Excretions_words_clean.csv', col_names = F)
Academics_clean <- read_csv('data/Academics_words_clean.csv', col_names = F)
Death_clean <- read_csv('data/Death_words_clean.csv', col_names = F)

summary <- read_csv('data/label_summary.csv') %>% 
  mutate(avg_words = round(avg_words))

kable(summary, align=c(rep('c',times=4)))
```

<br>

#### **Note**: a label of "None" means the text did not exhibit a taboo. 

<br>

```{r, message=FALSE, echo=FALSE, warning=FALSE}
######## Create Word Counts for EACH Label #################
word_count <- tibble(words = names(table(all_tokens)), count = table(all_tokens)) %>% 
  mutate(all_perc_total = round(count / dim(.)[1], 4)) %>% 
  filter(!words %in% stopwords('english')) %>%
  arrange(desc(count))

None_clean <- tibble(None_words = names(table(None_clean)), count = table(None_clean)) %>% 
  mutate(None_perc_total = round(count / dim(.)[1], 4)) %>% 
  arrange(desc(count))

Sex_clean <- tibble(Sex_words = names(table(Sex_clean)), count = table(Sex_clean)) %>% 
  mutate(Sex_perc_total = round(count / dim(.)[1], 4)) %>% 
  arrange(desc(count))

Mental_Health_clean <- tibble(Mental_words = names(table(Mental_Health_clean)), count = table(Mental_Health_clean)) %>% 
  mutate(Mental_perc_total = round(count / dim(.)[1], 4)) %>% 
  arrange(desc(count))

Money_Financial_clean <- tibble(Money_words = names(table(Money_Financial_clean)), count = table(Money_Financial_clean)) %>% 
  mutate(Money_perc_total = round(count / dim(.)[1], 4)) %>% 
  arrange(desc(count))

Medical_clean <- tibble(Medical_words = names(table(Medical_clean)), count = table(Medical_clean)) %>% 
  mutate(Medical_perc_total = round(count / dim(.)[1], 4)) %>% 
  arrange(desc(count))

Drugs_clean <- tibble(Drugs_words = names(table(Drugs_clean)), count = table(Drugs_clean)) %>% 
  mutate(Drugs_perc_total = round(count / dim(.)[1], 4)) %>% 
  arrange(desc(count))

Race_ProtectedGroups_clean <- tibble(Race_words = names(table(Race_ProtectedGroups_clean)), count = table(Race_ProtectedGroups_clean)) %>% 
  mutate(Race_perc_total = round(count / dim(.)[1], 4)) %>% 
  arrange(desc(count))

# Excretions <- tibble(Excretions_words = names(table(Excretions)), count = table(Excretions)) %>% 
#   mutate(Excretions_perc_total = round(count / dim(.)[1], 4)) %>% 
#   arrange(desc(count))

Academics_clean <- tibble(Academics_words = names(table(Academics_clean)), count = table(Academics_clean)) %>% 
  mutate(Academics_perc_total = round(count / dim(.)[1], 4)) %>% 
  arrange(desc(count))

Death_clean <- tibble(Death_words = names(table(Death_clean)), count = table(Death_clean)) %>% 
  mutate(Death_perc_total = round(count / dim(.)[1], 4)) %>% 
  arrange(desc(count))
```


```{r, message=FALSE, echo=FALSE, warning=FALSE}
word_count <- tibble(words = names(table(all_tokens)), count = table(all_tokens)) %>% 
  mutate(all_perc_total = round(count / dim(.)[1], 4)) %>% 
  filter(!words %in% stopwords('english')) %>%
  arrange(desc(count))

None <- tibble(None_words = names(table(None)), count = table(None)) %>% 
  mutate(None_perc_total = round(count / dim(.)[1], 4)) %>% 
  arrange(desc(count))

Sex <- tibble(Sex_words = names(table(Sex)), count = table(Sex)) %>% 
  mutate(Sex_perc_total = round(count / dim(.)[1], 4)) %>% 
  arrange(desc(count))

Mental_Health <- tibble(Mental_words = names(table(Mental_Health)), count = table(Mental_Health)) %>% 
  mutate(Mental_perc_total = round(count / dim(.)[1], 4)) %>% 
  arrange(desc(count))

Money_Financial <- tibble(Money_words = names(table(Money_Financial)), count = table(Money_Financial)) %>% 
  mutate(Money_perc_total = round(count / dim(.)[1], 4)) %>% 
  arrange(desc(count))

Medical <- tibble(Medical_words = names(table(Medical)), count = table(Medical)) %>% 
  mutate(Medical_perc_total = round(count / dim(.)[1], 4)) %>% 
  arrange(desc(count))

Drugs <- tibble(Drugs_words = names(table(Drugs)), count = table(Drugs)) %>% 
  mutate(Drugs_perc_total = round(count / dim(.)[1], 4)) %>% 
  arrange(desc(count))

Race_ProtectedGroups <- tibble(Race_words = names(table(Race_ProtectedGroups)), count = table(Race_ProtectedGroups)) %>% 
  mutate(Race_perc_total = round(count / dim(.)[1], 4)) %>% 
  arrange(desc(count))

# Excretions <- tibble(Excretions_words = names(table(Excretions)), count = table(Excretions)) %>% 
#   mutate(Excretions_perc_total = round(count / dim(.)[1], 4)) %>% 
#   arrange(desc(count))

Academics <- tibble(Academics_words = names(table(Academics)), count = table(Academics)) %>% 
  mutate(Academics_perc_total = round(count / dim(.)[1], 4)) %>% 
  arrange(desc(count))

Death <- tibble(Death_words = names(table(Death)), count = table(Death)) %>% 
  mutate(Death_perc_total = round(count / dim(.)[1], 4)) %>% 
  arrange(desc(count))



########### i words
i_words <- c('i', "i've", "i'd", "i'm", "i'll")

None_i <- sum(filter(None, None_words %in% i_words)$None_perc_total)
Sex_i <- sum(filter(Sex, Sex_words %in% i_words)$Sex_perc_total)
Mental_i <- sum(filter(Mental_Health, Mental_words %in% i_words)$Mental_perc_total)
Money_i <- sum(filter(Money_Financial, Money_words %in% i_words)$Money_perc_total)
Medical_i <- sum(filter(Medical, Medical_words %in% i_words)$Medical_perc_total)
Drugs_i <- sum(filter(Drugs, Drugs_words %in% i_words)$Drugs_perc_total)
Race_i <- sum(filter(Race_ProtectedGroups, Race_words %in% i_words)$Race_perc_total)
# Excretions_i <- sum(filter(Excretions, Excretions_words %in% i_words)$Excretions_perc_total)
Academics_i <- sum(filter(Academics, Academics_words %in% i_words)$Academics_perc_total)
Death_i <- sum(filter(Death, Death_words %in% i_words)$Death_perc_total)

summary$i_words <- c(None_i, Sex_i, Mental_i, Money_i, Medical_i, Drugs_i, Race_i
                     # , Excretions_i                     
                     , Academics_i, Death_i)


########## You Words ########################
u_words <- c('you', "u", "ur", "your", "youre", "you're", "you'll", "you'd")

# unique(all_tokens) %>% arrange(all_tokens) %>% View()
None_u <- sum(filter(None, None_words %in% u_words)$None_perc_total)
Sex_u <- sum(filter(Sex, Sex_words %in% u_words)$Sex_perc_total)
Mental_u <- sum(filter(Mental_Health, Mental_words %in% u_words)$Mental_perc_total)
Money_u <- sum(filter(Money_Financial, Money_words %in% u_words)$Money_perc_total)
Medical_u <- sum(filter(Medical, Medical_words %in% u_words)$Medical_perc_total)
Drugs_u <- sum(filter(Drugs, Drugs_words %in% u_words)$Drugs_perc_total)
Race_u <- sum(filter(Race_ProtectedGroups, Race_words %in% u_words)$Race_perc_total)
# Excretions_u <- sum(filter(Excretions, Excretions_words %in% u_words)$Excretions_perc_total)
Academics_u <- sum(filter(Academics, Academics_words %in% u_words)$Academics_perc_total)
Death_u <- sum(filter(Death, Death_words %in% u_words)$Death_perc_total)

summary$u_words <- c(None_u, Sex_u, Mental_u, Money_u, Medical_u, Drugs_u, Race_u, Academics_u, Death_u)

summary <- summary %>% 
  mutate(i_to_u_ratio = i_words / u_words)


####### Top Words ################
top_words <- 5
top_500_words <- bind_cols(None_clean[1:top_words,1]
                              , Sex_clean[1:top_words,1]
                            , Mental_Health_clean[1:top_words,1]
                            , Money_Financial_clean[1:top_words,1]
                            , Medical_clean[1:top_words,1]
                            , Drugs_clean[1:top_words,1]
                            , Race_ProtectedGroups_clean[1:top_words,1]
                            # , Excretions[1:top_words,1]
                            , Academics_clean[1:top_words,1]
                            , Death_clean[1:top_words,1])
```

<br>

### Top 5 words in each category

```{r, message=FALSE, echo=FALSE, warning=FALSE}
top_500_words %>% rename(None = None_words
                         ,Sex = Sex_words
                         ,Mental = Mental_words
                         ,Money = Money_words
                         ,Medical = Medical_words
                         ,Drugs = Drugs_words
                         ,Race = Race_words
                         ,Academics = Academics_words
                         ,Death = Death_words) %>% 
  kable()
```

<br>

### Trying to measure narcissism...

```{r, message=FALSE, echo=FALSE, warning=FALSE, fig.height = 8, fig.width = 8, fig.align = "center"}
graph_summary <- summary %>% gather()
labels <- filter(graph_summary, key == 'label')$value

graph_summary2 <- graph_summary %>%
  mutate(value = round(as.double(value), 4)
         ,label = rep(labels, nrow(.)/9)) %>%
  filter(key %in% c('i_words', 'u_words'))

# Plot3
# ggplot(graph_summary2, aes(x = key, y = value)) +
#   geom_bar(stat = 'identity', aes(fill = key)) +
#   coord_flip() +
#   facet_wrap(~ label) +
#   ggtitle("Number of 'I-words' vs Number of 'U-words'") +
#   theme_economist_white()
```

**Note**:
*I-words = I, I'd, I've, I'll, I'm
*U-words = You, Your, You're, Youre, You'll, You'd, U, Ur

<br>

```{r, message=FALSE, echo=FALSE, warning=FALSE, fig.height = 8, fig.width = 8, fig.align = "center"}
graph_summary3 <- graph_summary %>% 
  mutate(value = round(as.double(value), 4)
         ,label = rep(labels, nrow(.)/9)) %>% 
  filter(key %in% c('i_to_u_ratio'))

# Plot4
ggplot(graph_summary2, aes(x = reorder(label, value), y = value)) +
  geom_bar(stat = 'identity', fill = 'black') +
  coord_flip()+
  ggtitle("Ratio of 'I-words' to 'U-words'") +
  theme_fivethirtyeight()
```

<br>

```{r, message=FALSE, echo=FALSE, warning=FALSE}
############## Sentiment Analysis ######################


afinn_dict <- get_sentiments("afinn") %>% rename('afinn' = 'score')

bing_dict <- get_sentiments("bing") %>% 
  rename('bing' = 'sentiment') %>% 
  mutate(bing = ifelse(bing == 'negative', 0, ifelse(bing == 'positive', 1, NA))
         ,bing = as.integer(bing))
  
nrc_dict <- get_sentiments("nrc") %>% rename('nrc' = 'sentiment')

None_clean <- None_clean %>% 
  left_join(afinn_dict, by = c('None_words' = 'word')) %>% 
  left_join(bing_dict, by = c('None_words' = 'word')) %>% 
  left_join(nrc_dict, by = c('None_words' = 'word'))

Sex_clean <- Sex_clean %>% 
  left_join(afinn_dict, by = c('Sex_words' = 'word')) %>% 
  left_join(bing_dict, by = c('Sex_words' = 'word')) %>% 
  left_join(nrc_dict, by = c('Sex_words' = 'word'))

Mental_Health_clean <- Mental_Health_clean %>% 
  left_join(afinn_dict, by = c('Mental_words' = 'word')) %>% 
  left_join(bing_dict, by = c('Mental_words' = 'word')) %>% 
  left_join(nrc_dict, by = c('Mental_words' = 'word'))

Money_Financial_clean <- Money_Financial_clean %>% 
  left_join(afinn_dict, by = c('Money_words' = 'word')) %>% 
  left_join(bing_dict, by = c('Money_words' = 'word')) %>% 
  left_join(nrc_dict, by = c('Money_words' = 'word'))

Medical_clean <- Medical_clean %>% 
  left_join(afinn_dict, by = c('Medical_words' = 'word')) %>% 
  left_join(bing_dict, by = c('Medical_words' = 'word')) %>% 
  left_join(nrc_dict, by = c('Medical_words' = 'word'))

Drugs_clean <- Drugs_clean %>% 
  left_join(afinn_dict, by = c('Drugs_words' = 'word')) %>% 
  left_join(bing_dict, by = c('Drugs_words' = 'word')) %>% 
  left_join(nrc_dict, by = c('Drugs_words' = 'word'))

Race_ProtectedGroups_clean <- Race_ProtectedGroups_clean %>% 
  left_join(afinn_dict, by = c('Race_words' = 'word')) %>% 
  left_join(bing_dict, by = c('Race_words' = 'word')) %>% 
  left_join(nrc_dict, by = c('Race_words' = 'word'))

# Excretions <- Excretions %>% 
#   left_join(afinn_dict, by = c('Excretions_words' = 'word')) %>% 
#   left_join(bing_dict, by = c('Excretions_words' = 'word')) %>% 
#   left_join(nrc_dict, by = c('Excretions_words' = 'word'))

Academics_clean <- Academics_clean %>% 
  left_join(afinn_dict, by = c('Academics_words' = 'word')) %>% 
  left_join(bing_dict, by = c('Academics_words' = 'word')) %>% 
  left_join(nrc_dict, by = c('Academics_words' = 'word'))

Death_clean <- Death_clean %>% 
  left_join(afinn_dict, by = c('Death_words' = 'word')) %>% 
  left_join(bing_dict, by = c('Death_words' = 'word')) %>% 
  left_join(nrc_dict, by = c('Death_words' = 'word'))

word_count <- word_count %>% 
  left_join(afinn_dict, by = c('words' = 'word')) %>% 
  left_join(bing_dict, by = c('words' = 'word')) %>% 
  left_join(nrc_dict, by = c('words' = 'word'))


########### AFINN
mean_afinn <- bind_cols(select(filter(None_clean, !is.na(afinn)), None_words, afinn) %>% 
                          unique() %>% 
                          summarise(None = mean(afinn))
          ,select(filter(Sex_clean, !is.na(afinn)), Sex_words, afinn) %>% 
            unique() %>% 
            summarise(Sex = mean(afinn))
          ,select(filter(Mental_Health_clean, !is.na(afinn)), Mental_words, afinn) %>% 
            unique() %>% 
            summarise(Mental_Health = mean(afinn))
          ,select(filter(Money_Financial_clean, !is.na(afinn)), Money_words, afinn) %>% 
            unique() %>% 
            summarise(Money_Financial = mean(afinn))
          ,select(filter(Medical_clean, !is.na(afinn)), Medical_words, afinn) %>% 
            unique() %>% 
            summarise(Medical = mean(afinn))
          ,select(filter(Drugs_clean, !is.na(afinn)), Drugs_words, afinn) %>% 
            unique() %>% 
            summarise(Drugs = mean(afinn))
          ,select(filter(Race_ProtectedGroups_clean, !is.na(afinn)), Race_words, afinn) %>% 
            unique() %>% 
            summarise(Race_ProtectedGroups = mean(afinn))
          # ,select(filter(Excretions, !is.na(afinn)), Excretions_words, afinn) %>% 
          #   unique() %>% 
          #   summarise(Excretions = mean(afinn))
          ,select(filter(Academics_clean, !is.na(afinn)), Academics_words, afinn) %>% 
            unique() %>% 
            summarise(Academics = mean(afinn))
          ,select(filter(Death_clean, !is.na(afinn)), Death_words, afinn) %>% 
            unique() %>% 
            summarise(Death = mean(afinn))) %>% 
  gather(key = 'label', value = 'mean_afinn')


summary <- summary %>% 
  inner_join(mean_afinn, by = c('label'))



######## BING
mean_bing <- bind_cols(select(filter(None_clean, !is.na(bing)), None_words, bing) %>% 
                          unique() %>% 
                          summarise(None = mean(bing))
                        ,select(filter(Sex_clean, !is.na(bing)), Sex_words, bing) %>% 
                          unique() %>% 
                          summarise(Sex = mean(bing))
                        ,select(filter(Mental_Health_clean, !is.na(bing)), Mental_words, bing) %>% 
                          unique() %>% 
                          summarise(Mental_Health = mean(bing))
                        ,select(filter(Money_Financial_clean, !is.na(bing)), Money_words, bing) %>% 
                          unique() %>% 
                          summarise(Money_Financial = mean(bing))
                        ,select(filter(Medical_clean, !is.na(bing)), Medical_words, bing) %>% 
                          unique() %>% 
                          summarise(Medical = mean(bing))
                        ,select(filter(Drugs_clean, !is.na(bing)), Drugs_words, bing) %>% 
                          unique() %>% 
                          summarise(Drugs = mean(bing))
                        ,select(filter(Race_ProtectedGroups_clean, !is.na(bing)), Race_words, bing) %>% 
                          unique() %>% 
                          summarise(Race_ProtectedGroups = mean(bing))
                        # ,select(filter(Excretions, !is.na(bing)), Excretions_words, bing) %>% 
                          # unique() %>% 
                          # summarise(Excretions = mean(bing))
                        ,select(filter(Academics_clean, !is.na(bing)), Academics_words, bing) %>% 
                          unique() %>% 
                          summarise(Academics = mean(bing))
                        ,select(filter(Death_clean, !is.na(bing)), Death_words, bing) %>% 
                          unique() %>% 
                          summarise(Death = mean(bing))) %>% 
  gather(key = 'label', value = 'mean_bing')

summary <- summary %>% 
  inner_join(mean_bing, by = c('label'))



################# NRC #############################
None_nrc <- filter(None_clean, !is.na(nrc)) %>% count(nrc, sort = T) %>% rename('None' = 'n')
Sex_nrc <- filter(Sex_clean, !is.na(nrc)) %>% count(nrc, sort = T) %>% rename('Sex' = 'n')
Mental_nrc <- filter(Mental_Health_clean, !is.na(nrc)) %>% count(nrc, sort = T) %>% rename('Mental_Health' = 'n')
Money_nrc <- filter(Money_Financial_clean, !is.na(nrc)) %>% count(nrc, sort = T) %>% rename('Money_Financial' = 'n')
Medical_nrc <- filter(Medical_clean, !is.na(nrc)) %>% count(nrc, sort = T) %>% rename('Medical' = 'n')
Drugs_nrc <- filter(Drugs_clean, !is.na(nrc)) %>% count(nrc, sort = T) %>% rename('Drugs' = 'n')
Race_nrc <- filter(Race_ProtectedGroups_clean, !is.na(nrc)) %>% count(nrc, sort = T) %>% rename('Race_ProtectedGroups' = 'n')
# Excretions_nrc <- filter(Excretions_clean, !is.na(nrc)) %>% count(nrc, sort = T) %>% rename('Excretions' = 'n')
Academics_nrc <- filter(Academics_clean, !is.na(nrc)) %>% count(nrc, sort = T) %>% rename('Academics' = 'n')
Death_nrc <- filter(Death_clean, !is.na(nrc)) %>% count(nrc, sort = T) %>% rename('Death' = 'n')


nrc_summary <- inner_join(None_nrc, Sex_nrc, by = c('nrc')) %>% 
                  left_join(Mental_nrc, by = c('nrc')) %>% 
                  left_join(Money_nrc, by = c('nrc')) %>% 
                  left_join(Medical_nrc, by = c('nrc')) %>% 
                  left_join(Drugs_nrc, by = c('nrc')) %>% 
                  left_join(Race_nrc, by = c('nrc')) %>% 
                  # left_join(Excretions_nrc, by = c('nrc')) %>% 
                  left_join(Academics_nrc, by = c('nrc')) %>% 
                  left_join(Death_nrc, by = c('nrc')) 


nrc_col_sums <- as_tibble(cbind('label' = names(nrc_summary)[-1]
          , 'total_nrc' = colSums(nrc_summary[,-1]))) %>% 
  mutate(total_nrc = as.integer(total_nrc))


nrc_summary <- as_tibble(cbind(label = names(nrc_summary), t(nrc_summary))) %>% 
  rename(., 'negative' = 'V1'
         ,'positive' = 'V2'
         ,'trust' = 'V3'
         ,'fear' = 'V4'
         ,'sadness' = 'V5'
         ,'anger' = 'V6'
         ,'anticipation' = 'V7'
         ,'joy' = 'V8'
         ,'disgust' = 'V9'
         ,'surprise' = 'V10') %>% 
  filter(label != 'nrc') %>% 
  mutate(negative = as.integer(negative)
         ,positive = as.integer(positive)
         ,trust = as.integer(trust)
         ,fear = as.integer(fear)
         ,sadness = as.integer(sadness)
         ,anger = as.integer(anger)
         ,anticipation = as.integer(anticipation)
         ,joy = as.integer(joy)
         ,disgust = as.integer(disgust)
         ,surprise = as.integer(surprise))


nrc_summary_perc <- as_tibble(sweep(nrc_summary[,-1] %>% as.matrix(), 1, nrc_col_sums[,-1] %>% as.matrix(), '/')) %>% 
  mutate(label = nrc_summary$label)

summary <- summary %>% 
  inner_join(nrc_summary_perc, by = c('label'))
```

<br>

### Sentiments...

<br>

```{r, message=FALSE, echo=FALSE, warning=FALSE, fig.height = 8, fig.width = 8, fig.align = "center"}
graph_summary <- summary %>% gather()
labels <- filter(graph_summary, key == 'label')$value

graph_summary1 <- graph_summary %>% 
  mutate(value = round(as.double(value), 4)
    ,label = rep(labels, nrow(.)/9)) %>%   
  filter(!key %in% c('label', 'num_words', 'num_lines', 'avg_words', 'i_words', 'u_words'
                     , 'i_to_u_ratio', 'mean_afinn', 'mean_bing'))


# Plot1
# ggplot(graph_summary1, aes(x = label, y = value)) +
#   geom_bar(stat = 'identity', fill = 'black') +
#   coord_flip() +
#   facet_wrap(~ key) +
#   ggtitle("Category by Sentiment") +
#   theme_economist()
```

<br>

```{r, message=FALSE, echo=FALSE, warning=FALSE, fig.height = 8, fig.width = 8, fig.align = "center"}
# Plot2
ggplot(graph_summary1, aes(x = key, y = value)) +
  geom_bar(stat = 'identity', fill = 'black') +
  coord_flip() +
  facet_wrap(~ label) +
  ggtitle("Sentiment by Category") +
  theme_economist()
```

<br>

## Topic Modeling

```{r, message=FALSE, echo=FALSE, warning=FALSE}
######## Create a corpus ##########################
dfCorpus2 <- VCorpus(VectorSource(fcb_data$text)) # words


############ Pre-process #######################

dfCorpus2 <- tm_map(dfCorpus2, stripWhitespace)
dfCorpus2 <- tm_map(dfCorpus2, removePunctuation)
dfCorpus2 <- tm_map(dfCorpus2, removeNumbers)
dfCorpus2 <- tm_map(dfCorpus2, content_transformer(tolower))
dfCorpus2 <- tm_map(dfCorpus2, removeWords, stopwords("english"))
dfCorpus2 <- tm_map(dfCorpus2, stemDocument)

myStopwords <- c('can', 'say', 'one', 'way', 'use', 'also', 'howev', 'tell', 'will', 'much', 'take'
                 ,'tend', 'even', 'like', 'particular', 'rather', 'said', 'get', 'well', 'make', 'ask', 'come'
                 ,'end', 'first', 'two', 'help', 'often', 'may', 'might', 'see', 'someth', 'thing', 'point'
                 ,'post', 'look', 'right', 'now', 'think', 'anoth', 'put', 'set', 'new', 'want', 'sure', 'kind'
                 ,'larg', 'yes', 'day', 'etc', 'quit', 'sinc', 'attempt', 'lack', 'seen', 'awar', 'littl', 'ever'
                 ,'moreov', 'though', 'found', 'abl', 'enough', 'far', 'earli', 'away', 'achiev', 'draw', 'last'
                 ,'brief', 'bit', 'entir', 'lot', 'wish', 'what', 'just', 'that', 'let', 'dont', 'cant', 'still')

dfCorpus2 <- tm_map(dfCorpus2, removeWords, myStopwords)


################# Create Document-Term-Matrix #####################
dtm <- DocumentTermMatrix(dfCorpus2)
dtm2 <- removeSparseTerms(dtm, 0.985)

rowTotals <- apply(dtm2, 1, sum)
dtm3 <- dtm2[rowTotals > 0,]
fcb_data2 <- fcb_data[rowTotals > 0,]
```

```{r, message=FALSE, echo=FALSE, warning=FALSE, fig.height = 13, fig.width = 13, fig.align = "center"}
topic_search <- read.csv('data/topic_search.csv')
FindTopicsNumber_plot(topic_search)
```


```{r, message=FALSE, echo=FALSE, warning=FALSE, fig.height = 11, fig.width = 11, fig.align = "center"}
################## Create LDA ########################


burnin <- 4000
iter <- 2000
thin <- 500
seed <- list(2003, 5, 63, 100001, 765)
nstart <- 5
k <- 35

lda_out <- LDA(dtm, k, method = 'Gibbs'
               , control = list(nstart = nstart, seed = seed, burnin = burnin, iter = iter, thin = thin))
```

```{r, message=FALSE, echo=FALSE, warning=FALSE, fig.height = 11, fig.width = 11, fig.align = "center"}
# Create word probabilities for each document
lda_word_probs <- tidy(lda_out, matrix = 'beta')

# Displays word probabilities
lda_top_terms <- lda_word_probs %>%
  group_by(topic) %>%
  top_n(6, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

lda_top_terms %>%
  mutate(term = reorder(term, beta)) %>%
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip() +
  ggtitle("Top Words per Topic")
```

<br>

```{r, message=FALSE, echo=FALSE, warning=FALSE}
# View each document's topic
topics <- topics(lda_out)

if (length(topics) == length(fcb_data$text)) { 
  
  fcb_data$topic = topics 
  
  fcb_data <- fcb_data %>% group_by(label)
  table1 <- table(filter(fcb_data, label != 'None')$label, filter(fcb_data, label != 'None')$topic)
  table2 <- table(filter(fcb_data, label == 'None')$label, filter(fcb_data, label == 'None')$topic)
  }
```

### Do any of our categories fall into our topics?

```{r, message=FALSE, echo=FALSE, warning=FALSE}
kable(table1)
```

<br>

### Can we identify any clear, new topics?

```{r, message=FALSE, echo=FALSE, warning=FALSE}
kable(table2)
```